2.4 PRNT50

### 2025-04-17 2_scripts/2.3 Prob Model for PCR pos.qmd
Update figures for the manuscript.
Updated Fig 1 for rev 1

```{r}
# making the plot, either those codes will work
p03.3<-tb_alberta %>%
  ggplot(aes(x=samplemonth, y=prop, colour=study, linetype=study)) +
  geom_point() +
  geom_line()  +
  theme_bw() + 
  xlab("Time of Sample Collection") + 
  ylab("Sero-prevalence")+ 
  scale_colour_manual("",   values = c("red", "red", "blue", "blue"))+
  scale_linetype_manual("", values=c(1,3,1,3))

# use this chunk to skip the paste()
p03.lab<-c("APL (raw)", "CBS (raw)", 
           "APL (transformed)", "CBS (transformed)")
p03.3<-tb_alberta %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(data, raw),
                                    linetype=interaction(data, raw))) +
  geom_point() +
  geom_line()  +
  theme_bw() +
  xlab("Time of Sample Collection") + 
  ylab("Sero-prevalence")+ 
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p03.lab)+
  scale_linetype_manual("", values=c(1,1,3,3), labels = p03.lab) +
  theme(legend.position="top")+
  guides(color = guide_legend(nrow = 2))

@@

```{r}
# rebuild the figure
p03.5lab<-c("APL (raw)", "CBS (raw)", 
            "APL (RG-Bayesian)", "CBS (RG-Bayesian)")

p03.5<-tb_ab_rg %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(data,rg),
                                    linetype=interaction(data,rg))) +
  geom_point() +
  geom_line()  +
  geom_errorbar(aes(ymin=rg_lower, ymax=rg_upper), width=0.05)+
  theme_bw() + 
  xlab("Time of Sample Collection") + 
  ylab("Sero-prevalence") +
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p03.5lab) +
  scale_linetype_manual("", values=c(1,1,3,3), labels = p03.5lab) +
  theme(legend.position="top")+
  guides(color = guide_legend(nrow = 2))

@@

>>>>

```{r}
# making the plot, either those codes will work
p03.3<-tb_alberta %>%
  ggplot(aes(x=samplemonth, y=prop, colour=study, linetype=study)) +
  geom_point() +
  geom_line()  +
  theme_bw() + 
  xlab("Time of Sample Collection") + 
  ylab("Seroprevalence")+ 
  scale_colour_manual("",   values = c("red", "red", "blue", "blue"))+
  scale_linetype_manual("", values=c(1,3,1,3))

# use this chunk to skip the paste()
p03.lab<-c("APL Abbott (actual)", "CBS Roche (actual)", 
           "APL Roche (transformed)", "CBS Abbott (transformed)")
p03.3<-tb_alberta %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(data, raw),
                                    linetype=interaction(data, raw))) +
  geom_point() +
  geom_line()  +
  theme_bw() +
  xlab("Time of Sample Collection") + 
  ylab("Seroprevalence")+ 
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p03.lab)+
  scale_linetype_manual("", values=c(1,1,3,3), labels = p03.lab) +
  theme(legend.position="top")+
  guides(color = guide_legend(nrow = 2))

@@

```{r}
# rebuild the figure
p03.5lab<-c("APL Abbott (actual)", "CBS Roche (actual)", 
            "APL Abbott (RG-Bayesian)", "CBS Roche (RG-Bayesian)")

p03.5<-tb_ab_rg %>%
  ggplot(aes(x=samplemonth, y=prop, colour=interaction(data,rg),
                                    linetype=interaction(data,rg))) +
  geom_point() +
  geom_line()  +
  geom_errorbar(aes(ymin=rg_lower, ymax=rg_upper), width=0.05)+
  theme_bw() + 
  xlab("Time of Sample Collection") + 
  ylab("Seroprevalence") +
  scale_colour_manual("", values = c("red", "blue", "red", "blue"),
                      labels = p03.5lab) +
  scale_linetype_manual("", values=c(1,1,3,3), labels = p03.5lab) +
  theme(legend.position="top")+
  guides(color = guide_legend(nrow = 2))

@@

#### 3.6 Create fig panel for the manuscript
```{r}
# use cowplot package
p08.upper<-cowplot::plot_grid(p03.5  + ylab("Seroprevalence") +
                              ylim(0,0.8), 
                              p03.3  + ylab("") +
                              ylim(0,0.8)+
                              scale_y_continuous(breaks = c(0,0.2,0.4,0.6,0.8)),
                              nrow=1, align = "h",
                              labels = c("A", "B"))
p08.upper

png(file="../4_output/figs/Fig.1m Seroprevalence.png", 
    width=2400, height=1000, res=300)
p08.upper
dev.off()
```

### 2025-04-17 2_scripts/2.4 PRNT50.qmd
Updated Fig 1 for rev 1

png(file="../4_output/figs/Fig.4 Immunity.png", 
    width=2400, height=2000, res=300)
p09all
dev.off()
```
## 5. Additional analysis for manuscript
```{r}
# median age in CBS Alberta and APL
summary(CBSs_AB$age) 
summary(APLs$age) # age=0?

@@

#### PCR-verified test positivity:
```{r}
# How many test results are previously PCR-verified?

>>>>

png(file="../4_output/figs/Fig.4 Immunity.png", 
    width=2400, height=2000, res=300)
p09all
dev.off()
```
## 5. Additional analysis for manuscript

####  5.1 Some desc analysis
```{r}
# median age in CBS Alberta and APL
summary(CBSs_AB$age) 
summary(APLs$age) # age=0?

@@

#### 5.2 PCR-verified test positivity:
We did this analysis as suggested by the reviewer-1
```{r}
# How many test results are previously PCR-verified?
